```{r}
getwd()
list.files()
pf<- read.csv("pseudo_facebook.tsv",sep='\t')
names(pf)
```
###histogram of users' birthdays
```{r}
install.packages('ggplot2')
library(ggplot2)
names(pf)
ggplot(aes(x=dob_day),data=pf)+
  geom_histogram(binwidth = 1)
  scale_x_continuous(breaks = 1:31)
```
```{r}
ggplot(aes(x=dob_day),data=pf)+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month, ncol=4)
```
```{r}
ggplot(aes(x=friend_count),data=pf)+
  geom_histogram(binwidth = 25)+
  scale_x_continuous(limits = c(0,1000),breaks = seq(0,1000,50))+
  facet_wrap(~gender)
```
```{r}
ggplot(aes(x=friend_count),data=subset(pf, !is.na(gender)))+
  geom_histogram(binwidth = 25)+
  scale_x_continuous(limits = c(0,1000),breaks = seq(0,1000,50))+
  facet_wrap(~gender)
```

```{r}
table(pf$gender)
```
##statistics 'by' gender
```{r}
table(pf$gender)
by(pf$friend_count,pf$gender,summary)
```
###17 time
```{r}
ggplot(aes(x=tenure/365),data=pf)+
  geom_histogram(binwidth = .25,color='black', fill='#099DD9')
scale_x_continuous(breaks = seq(1,7,1),limits=c(0,7))
```
##18 labeling plots 
```{r}
ggplot(aes(x=tenure/365),data = pf,
       xlab='number of years using Facebook',
       ylab='number of users in sample')+
  geom_histogram(binwidth = .25,color='black', fill='#099DD9')+
  scale_x_continuous(breaks = seq(1,7,1), lim=c(0,7))
```
###user ages solution
```{r}
ggplot(aes(x=age), data=pf, binwidth=1)+
  geom_histogram(color='black', fill='#5760AB')
```
##tansforming data solution
```{r}
install.packages('gridExtra')
library(gridExtra)
p1<- ggplot(data = pf,aes(x=friend_count))+
  geom_histogram()
p2<- p1+scale_x_log10()
p3<- p1+scale_x_sqrt()
grid.arrange(p1,p2,p3,ncol=1)
```
##add a scaling layer
```{r}
logScale<- qplot(x=log10(friend_count),data=pf)
countScale<- ggplot(aes(x=friend_count),data = pf)+geom_histogram()+
  scale_x_log10()

grid.arrange(logScale,countScale,ncol=2)
```

##frequency Polygons(before we had histograms)
```{r}
ggplot(aes(x=friend_count,y=..count../sum(..count..)),data=subset(pf, !is.na(gender)))+
geom_freqpoly(aes(color=gender),binwidth=10)+
  scale_x_continuous(limits=c(0,1000), breaks = seq(0,1000,50))
```
##frequency Polygons Solution
```{r}
ggplot(aes(x=www_likes),data=subset(pf,!is.na(gender)))+
  geom_freqpoly(aes(color=gender))+
  scale_x_log10()
```
##www_likes on web
```{r}
by(pf$www_likes,pf$gender,sum)
```
##Box Plots
```{r}
ggplot(aes(x=gender,y=friend_count),data=subset(pf,!is.na(gender)))+ 
  geom_boxplot()+
  scale_y_continuous(limits = c(0,1000))
```
##Box Plots
```{r}
ggplot(aes(x=gender,y=friend_count),data=subset(pf,!is.na(gender)))+ 
  geom_boxplot()+
  coord_cartesian(ylim=c(0,250))
by(pf$friend_count,pf$gender,summary)
```
```{r}
ggplot(aes(x=gender,y=friendships_initiated),data=subset(pf,!is.na(gender)))+ 
  geom_boxplot()+
  coord_cartesian(ylim=c(0,150))
by(pf$friendships_initiated,pf$gender,summary)
```
##getting logical 
```{r}
summary(pf$mobile_likes)
summary(pf$mobile_likes>0)

pf$mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes>0,1,0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)
sum(pf$mobile_check_in==1)/length(pf$mobile_check_in)
```
###1
```{r}
library(ggplot2)
data(diamonds)

dim(diamonds)
str(diamonds)
str(diamonds$color)
```
###2
```{r}
ggplot(diamonds)+geom_histogram(aes(x=price),color='black',fill='blue')
 
```
###3
```{r}
summary(diamonds$price)
```
###4
```{r}
nrow(subset(diamonds,price<500))
nrow(subset(diamonds,price<250))
nrow(subset(diamonds,price>=15000))
```
###5
```{r}
ggplot(diamonds)+
  geom_histogram(aes(x=price),binwidth = 5,color='black',fill='lightgreen')+
  scale_x_continuous(limits=c(0,1200))
```
###6
```{r}
ggplot(diamonds)+
  geom_histogram(aes(x=price),binwidth = 5,color='black',fill='lightblue')+
  facet_wrap(~cut)
```
###7
```{r}
summary(diamonds$price)
#diamonds[diamonds$price==18823,]
#diamonds[diamonds$price==326,]
by(diamonds$price,diamonds$cut,summary)
```
###8
```{r}
ggplot(aes(x=price),data=diamonds)+
  geom_histogram()+
  facet_wrap(~cut,scales = 'free_y',ncol=2)
```
##9
```{r}
ggplot(aes(x=price/carat),data=diamonds)+
  geom_histogram(binwidth = 0.05,color='blue',fill='lightblue')+
  scale_x_log10()+
  facet_wrap(~cut,ncol = 2)
```
##10
```{r}
by(diamonds$price,diamonds$clarity,summary)
ggplot(aes(x=clarity,y=price),data=diamonds)+
  geom_boxplot()+
  coord_cartesian(ylim=c(0,10000))
  scale_y_continuous(breaks = seq(0,10000,2000))

```
##11:
```{r}
by(diamonds$price,diamonds$color,summary)
IQR(subset(diamonds, color=='J')$price)
IQR(subset(diamonds, color=='D')$price)
```
##12
```{r}
ggplot(aes(x=color,y=price/carat),data=diamonds)+
  geom_boxplot()+
  ggtitle('price per carat by color')
```
##13
```{r}
ggplot(aes(x=carat),data=diamonds)+
  geom_freqpoly(binwidth = 0.02)+
  scale_x_continuous(limits = c(0,1.5),breaks = seq(0,1.5,0.1))
```
```{r}
install.packages("rworldmap")
install.packages("RColorBrewer")
```

```{r}
#install.packages('reshape2')
library(reshape2)
library(ggplot2)
library(plyr)
library(rworldmap)
library(RColorBrewer)
data<-read.csv('marriage.csv',col.names = c('Country','1970','2005'))
data<- melt(data,id.vars=c('Country'))
names(data)<-c('Country','Year','Age')
data$Year<-gsub('X','',data$Year)
data$Year<-as.factor(data$Year)

data$Age <- gsub(",",".",data$Age)
data$Age <- as.numeric(data$Age)

data <- data[complete.cases(data),]
ggplot(data)+
  scale_y_continuous(breaks = seq(0,30,10))+
  coord_cartesian(ylim=c(20,30))+
  geom_boxplot(aes(x=Year,y=Age,fill=Year))+
  ggtitle('Average Marriage Age by Year')
```
```{r}
g20 <- c("Argentina","Australia", "Brazil","Canada","China","France",
                   "Germany", "India", "Indonesia","Italy", "Japan","Mexico",
                   "Russia", "Saudi Arabia", "South Africa",
                   "Turkey", "United Kingdom", "United States")
g20.data <- subset(data, Country %in% g20)
ggplot(g20.data)+
  geom_boxplot(aes(x=Country,y=Age,fill=Country))+
  ggtitle('the Average Aarriage Age of Woman in G20 Countries')+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
#load and cleaning data
library(lubridate)
birthdays <- read.csv("birthdays.csv")
birthdays$dates <- mdy(birthdays$dates)
birthdays$month <- month(birthdays$dates)
birthdays$day <- day(birthdays$dates)
#some basic analysis:
summary(birthdays)
table(birthdays$month)
table(birthdays$day)
##how many people share your birthday?
my<-subset(birthdays,month==02 & day==11)
nrow(my)
##which mongth contains the most number of birthdays?
ggplot(aes(x=month),data=birthdays)+
  geom_histogram(color='black',fill='blue',binwidth = 1)+
  scale_x_discrete()+
  scale_y_discrete()+
  ggtitle('birthdays in each month')
##how many birthdays are in each month?
table(birthdays$month)
##which day of the year has the most number of birthdays?
ggplot(aes(x=day),data=birthdays)+
  geom_histogram(color='black',fill='blue',binwidth = 1)+
  scale_x_discrete()+
  scale_y_discrete()+
  ggtitle('birthdays in each day')
##do you have at least 365 friends that have birthday on everyday of the year?
length(unique(birthdays$dates))
