Quality of Red Wine by TU YEMEI
========================================================
  
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.
#install.packages('COUNT')
#install.packages('GlobalOptions')
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
library(lattice)
library(MASS)
library(memisc)
library(COUNT)
library(msme)
library(sandwich)
library(GGally)
library(dplyr)
library(GlobalOptions)
library(graphics)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(message = FALSE,warning=FALSE,echo=FALSE)
```


```{r echo=FALSE, Load_the_Data}
# Load the Data
wine<-read.csv('wineQualityReds.csv')
names(wine)
summary(wine)
```

# Univariate Plots Section
#####At first, we can have an overview of the distribution of wine quality:
```{r echo=FALSE}
ggplot(aes(x=quality),data=wine)+
  geom_histogram(binwidth = 0.5)+
  scale_x_continuous(breaks = seq(0,10,1))+
  xlab('wine grade')+
  ylab('count')+
  ggtitle('Distribution of Red Wine Quality')
```

##### We can observe that the popular range of acid of red wine 
```{r echo=FALSE}
p1<-ggplot(aes(x=fixed.acidity),data=wine)+
  geom_histogram(binwidth = 0.5)+
  scale_x_continuous(breaks = seq(4,14,1))+
  xlim(4, quantile(wine$fixed.acidity, 0.95))+
  xlab('fixed acidity')
p2<-ggplot(aes(x=volatile.acidity,color=volatile.acidity),data=wine)+
  geom_histogram(binwidth = 0.05)+
  scale_x_continuous(breaks = seq(0.2,0.8,0.1),limits = c(0.2,0.8))+
  xlab('volatile acidity')
p3<-ggplot(aes(x=citric.acid),data=wine)+
  geom_histogram(binwidth = 0.02)+
  scale_x_continuous(limits = c(-0.02,0.23))
xlab('citric acid')
grid.arrange(p1,p2,p3,ncol=1)
```

##### I am confused about the distribution, I already made the binwidth to 0.5, but the distribution seems quite weird.


#####I want to have a view of the other chemical properties distribution 
```{r echo=FALSE}
p4<-ggplot(aes(x=residual.sugar ),data=wine)+
  geom_histogram(binwidth = 0.5)+
  scale_x_continuous(limits = c(0,5))+
  xlab('residual sugar ')
p5<-ggplot(aes(x=chlorides ),data=wine)+
  geom_histogram(binwidth = 0.01)+
  scale_x_continuous(limits=c(0.025,0.12))+
  xlab('chlorides')
p6<-ggplot(aes(x=free.sulfur.dioxide ),data=wine)+
  geom_histogram(binwidth = 2)+
  scale_x_continuous(limits = c(0,40))+
  xlab('free sulfur dioxide')
p7<-ggplot(aes(x=total.sulfur.dioxide ),data=wine)+
  geom_histogram(binwidth = 6)+
  scale_x_continuous(limits = c(0,100))+
  xlab('total sulfur dioxide')
p8<-ggplot(aes(x=pH ),data=wine)+
  geom_histogram(binwidth = 0.1)+
  scale_x_continuous(limits = c(2.75,3.7))+
  xlab('pH')
p9<-ggplot(aes(x=sulphates ),data=wine)+
  geom_histogram(binwidth = 0.1)+
  scale_x_continuous(limits = c(0.25,1.2))+
  xlab('sulphates')
p10<-ggplot(aes(x=alcohol ),data=wine)+
  geom_histogram(binwidth = 0.5)+
  scale_x_continuous(limits = c(9,13))+
  xlab('alcohol')
grid.arrange(p4,p5,p6,p7,p8,p9,p10,ncol=2)
```

#####make some adjustment to the chemical properties
```{r echo=FALSE}
p1<-ggplot(aes(x=residual.sugar ),data=wine)+
  geom_histogram(binwidth = 0.2)+
  xlab('residual sugar ')+
  scale_x_continuous(limits = c(1,3.5),breaks = seq(0,5,0.5))+
  xlim(0,quantile(wine$residual.sugar,0.95))+
  ggtitle('Residual Sugar Distribution')

p2<-ggplot(aes(x=chlorides),data=wine)+
  geom_histogram(binwidth = 0.01)+
  scale_x_continuous(limits=c(0,0.2),breaks = seq(-0.5,0.5,0.1))
xlab('chlorides')


grid.arrange(p1,p2,ncol=1)
```

##### The free sulfur dioxide and total sulfur dioxide is positively skewed 
```{r echo=FALSE}
p3<-ggplot(aes(x=free.sulfur.dioxide ),data=wine)+
  geom_histogram(binwidth = 1)+
  xlim(0,quantile(wine$free.sulfur.dioxide,0.95))+
  xlab('free sulfur dioxide')
p4<-ggplot(aes(x=total.sulfur.dioxide ),data=wine)+
  geom_histogram(binwidth = 5)+
  xlim(0,quantile(wine$total.sulfur.dioxide,0.95))+
  xlab('total sulfur dioxide')
grid.arrange(p3,p4,ncol=1)
```

# Univariate Analysis

#### What is the structure of your dataset?
######13varibles,1599 obervations 

#### What is/are the main feature(s) of interest in your dataset?
###### the quality is of highest interest, because it is related to other chemical properties.

#### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?
######I think three chemical varibles of acid, two varibles of sulfur can be combined as single varible, and with the other chemical properties.

#### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?
######some varibles have long tail, and i limit the x scale to the 95% in order to remove some outliers.


# Bivariate Plots Section
```{r echo=FALSE,fig.width = 15, fig.height = 15}
ggpairs(wine,upper = list(continuous = wrap("cor", size = 3)))
```

#####We can find the top 4factors related to quality is 'alcohol 0.476','volatile.acidity -0.391','sulphates 0.251, citric.acid 0.226' 

```{r echo=FALSE}
wine$quality_level<-cut(wine$quality,
                        c(2.5,3.5,4.5,5.5,6.5,7.5,8.5),
                        labels=c(1,2,3,4,5,6))
ggplot(aes(x=quality_level,y=alcohol),data=wine)+
  geom_boxplot(alpha=0.25)+
  geom_jitter(alpha=0.3,color='brown')
```

#####I want to add some lines to show the general trend
```{r echo=FALSE}
ggplot(aes(x=quality,y=alcohol),data=wine)+
  geom_point(color='brown',alpha=1/4,position='jitter')+
  geom_line(stat = 'summary',fun.y=quantile, fun.args=list(probs=.9),linetype=3,color='blue')+
  geom_line(stat = 'summary',fun.y=quantile, fun.args=list(probs=.5),linetype=2,color='black')+
  geom_line(stat = 'summary',fun.y=quantile, fun.args=list(probs=.1),linetype=4,color='orange')
```

#####In this plot, we can observe that alcohol inreases with the quality.

####Labeling quality with different levels & boxplot
##### I want to label quality of wine into several different category, thus I can use box plot to explore it.

```{r echo=FALSE}
wine$quality_level<-cut(wine$quality,
                        c(2.5,3.5,4.5,5.5,6.5,7.5,8.5),
                        labels=c(1,2,3,4,5,6))
```
```{r echo=FALSE}
ggplot(aes(quality_level,alcohol),data=wine)+
  geom_boxplot()+
  ggtitle('Wine quality VS Alcohol')
```

##### Make the same analysis for the other 3 factors and explore the plot

```{r echo=FALSE}
ggplot(aes(quality_level,volatile.acidity),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='brown')+
  ggtitle('Wine quality VS Volatile.acidity')
```

#####negative relationship between quality and volatile acidity 

```{r echo=FALSE}
ggplot(aes(quality_level,sulphates),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='blue')+
  ggtitle('Wine quality VS Sulphates')
```

####positive relationship 

```{r echo=FALSE}
ggplot(aes(alcohol,fill=quality_level),data=wine)+
  geom_histogram(binwidth = 0.5,alpha=0.7)+
  scale_fill_brewer(type='seq')
```

#####It is clearly that higher quality has higher content of alcohol.
#####Since there are six levels, and number of the highest and lowest level are too small to be observed clearly, I plan to combine two levels together, and divide the six levels into three wider levels: Low, Median, High.

```{r echo=FALSE}
wine$wide_level<-cut(wine$quality, c(2.5,4.5,6.5,8.5),
                     labels=c('Low','Medium','High'))
p1<-ggplot(aes(alcohol,fill=wide_level),data=wine)+
  geom_histogram(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
p2<-ggplot(aes(alcohol,fill=wide_level),data=wine)+
  geom_density(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
grid.arrange(p1,p2,ncol=1)
```

#####In this way, we can get a more clear overview of alcohol distribution and we can apply the same analysis to the other three factors.

```{r echo=FALSE}
p1<-ggplot(aes(volatile.acidity,fill=wide_level),data=wine)+
  geom_histogram(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
p2<-ggplot(aes(volatile.acidity,fill=wide_level),data=wine)+
  geom_density(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
grid.arrange(p1,p2,ncol=1)
```

##### Density performs better than histogram in volatile acidity analysis, since from the upper plot, we can only conclude that most wine in the 0.5-xais ,and from the lower plot, higher quality requires lower acidity 

```{r echo=FALSE}
p1<-ggplot(aes(citric.acid,fill=wide_level),data=wine)+
  geom_histogram(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
p2<-ggplot(aes(citric.acid,fill=wide_level),data=wine)+
  geom_density(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
grid.arrange(p1,p2,ncol=1)
```

#####Higher quality requires higher citric acid.

```{r echo=FALSE}
p1<-ggplot(aes(sulphates,fill=wide_level),data=wine)+
  geom_histogram(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
p2<-ggplot(aes(sulphates,fill=wide_level),data=wine)+
  geom_density(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
grid.arrange(p1,p2,ncol=1)
```

##### This plot is long tale which needs some function, I omit the top 1% of sulphates.

```{r echo=FALSE}
top_sulphates <- quantile(wine$sulphates,probs = 0.99)
sample1 <- subset(wine, wine$sulphates < top_sulphates)
ggplot(aes(sulphates,fill=wide_level),data=sample1)+
  geom_density(binwidth = 0.5,alpha=0.5)+
  scale_fill_brewer(type='seq')
```
```{r echo=FALSE}
library(dplyr)
quality_group<-group_by(wine,quality)
median_wine<-summarise(quality_group,
                       fixed.acidity = median(fixed.acidity),
                       volatile.acidity = median(volatile.acidity),
                       citric.acid = median(citric.acid),
                       residual.sugar = median(residual.sugar),
                       chlorides = median(chlorides),
                       free.sulfur.dioxide = median(free.sulfur.dioxide),
                       total.sulfur.dioxide = median(total.sulfur.dioxide),
                       density = median(density),
                       pH = median(pH),
                       sulphates = median(sulphates),
                       alcohol = median(alcohol),
                       n=n())

median_wine$fixed.acidity = 
  median_wine$fixed.acidity/max(median_wine$fixed.acidity)
median_wine$volatile.acidity = 
  median_wine$volatile.acidity/max(median_wine$volatile.acidity)
median_wine$citric.acid = 
  median_wine$citric.acid/max(median_wine$citric.acid)
median_wine$residual.sugar = 
  median_wine$residual.sugar/max(median_wine$residual.sugar)  
median_wine$chlorides = 
  median_wine$chlorides/max(median_wine$chlorides)
median_wine$pH=median_wine$pH/max(median_wine$pH)
median_wine$free.sulfur.dioxide = 
  median_wine$free.sulfur.dioxide/max(median_wine$free.sulfur.dioxide)
median_wine$total.sulfur.dioxide = median_wine$total.sulfur.dioxide/max(median_wine$total.sulfur.dioxide)
median_wine$density = 
  median_wine$density/max(median_wine$density)
median_wine$sulphates = 
  median_wine$sulphates/max(median_wine$sulphates)
median_wine$alcohol = median_wine$alcohol/max(median_wine$alcohol)
median_wine$quality_level<-cut(median_wine$quality,
                               c(2.5,3.5,4.5,5.5,6.5,7.5,8.5),
                               labels=c(1,2,3,4,5,6))
p1<-ggplot(aes(quality_level,fixed.acidity),data=median_wine)+
  geom_boxplot()
p2<-ggplot(aes(quality_level,volatile.acidity),data=median_wine)+
  geom_boxplot()
p3<-ggplot(aes(quality_level,citric.acid),data=median_wine)+
  geom_boxplot()
p4<-ggplot(aes(quality_level,residual.sugar),data=median_wine)+
  geom_boxplot()
p5<-ggplot(aes(quality_level,chlorides),data=median_wine)+
  geom_boxplot()
p6<-ggplot(aes(quality_level,pH),data=median_wine)+
  geom_boxplot()
p7<-ggplot(aes(quality_level,free.sulfur.dioxide),data=median_wine)+
  geom_boxplot() 
p8<-ggplot(aes(quality_level,total.sulfur.dioxide),data=median_wine)+
  geom_boxplot()
p9<-ggplot(aes(quality_level,density),data=median_wine)+
  geom_boxplot()
p10<-ggplot(aes(quality_level,alcohol),data=median_wine)+
  geom_boxplot()
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,ncol=3)
```

####Explore two main variables 
```{r echo=FALSE}
ggplot(wine, aes(x=citric.acid,y=volatile.acidity)) +
  geom_point(color='darkblue',alpha=1/2)+
  geom_smooth(color='orange')
```

###### We can have a overview of the trends of different variables 

# Bivariate Analysis

##### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

######At first, I calculate the Pearson Correlation of different variables, especilly focus on relationships with quality. And I explore more on top 4 factors influencing quality the most, it turns out that volatile acidity has a negative influence, while citric acid and alcohol have a positive influence on quality.

#####Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

######I made a plot to explore chemical properties, which is proved to have weak correlation with quality, and I find that three variables, fixed acidity,free sulfur dioxide and total sulfur dioxide present some peaks.

#####What was the strongest relationship you found?
###### The most strongest relatiship in my analysis is alcohol vs. quality, higher quality requires higher concentration of alcohol, I have not figuerd it out whether it is a causal relationship.  Furthermore, through statistic calculation, the alcohol variable is proved to be the most related variable.

# Multivariate Plots Section
######We already know that alcohol contributes a lot to the quality of wine, and now, I want to insert other variables to see if they contribute to the quality in other way.
```{r echo=FALSE}
ggplot(aes(x=alcohol,y=density,color=quality_level),data=wine)+
  geom_point(position='jitter',alpha=0.8)+
  scale_y_continuous(limits = c(0.992,1.002))+
  scale_x_continuous(limits = c(9,13))+
  scale_color_brewer(type='seq')
```

#####From the plot above, takes level-3 for example, it ranges from 0.9925-1.0000, which indicates that density contributes little to quality level, which the alcohol has a weak negative influence on density telling from the plot.

```{r echo=FALSE}
ggplot(aes(x=alcohol,y=sulphates),data=wine)+
  geom_point(position='jitter',alpha=0.5)+
  scale_x_continuous(limits = c(9,13))+
  scale_y_continuous(limits = c(0.3,1.2))+
  facet_wrap(~quality_level)+
  geom_smooth(method='lm',color='brown',size=0.5)
#scale_color_brewer(type='qual')
```

#####Since the plot is hard to explore, thus I use facet_wrap function to divide it. From the plot, We can infer that low quality between 1-3 lies around 0.5 in y-axis, while quality level of 4-6 tend to have higher y-axis, and also x-axis, thus higher quality wine have higher alcohol and sulphates.



```{r echo=FALSE}
ggplot(data = wine,
       aes(y = pH, x = alcohol
       )) +
  geom_point(alpha = 0.5) +
  # geom_smooth(method = "lm")  +
  facet_wrap(~quality_level) 
#scale_color_brewer(type='qual')
```

##### The influence of PH is not obvious 

```{r echo=FALSE}
ggplot(data = wine,
       aes(y = residual.sugar, x = alcohol)) +
  geom_point(alpha = 0.3,color='lightblue') +
  scale_x_continuous(limits = c(9,13.5))+
  scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",size=0.5)  +
  facet_wrap(~quality_level) +
  scale_color_brewer(type='qual')
```

##### Every quality level has a large range of y-axis, which means residual sugar has little influence on quality.


```{r echo=FALSE}
ggplot(data = wine,
       aes(y = total.sulfur.dioxide, x = alcohol
       )) +
  geom_point(position='jitter',alpha = 0.5,color='brown') +
  scale_x_continuous(limits = c(9,13.5))+
  scale_y_continuous(limits = c(10,150))+
  geom_smooth(method = "lm",size=0.3,color='black')  +
  facet_wrap(~quality_level) +
  scale_color_brewer(type='qual')
```

##### Lower total sulfur dioxide and higher alcohol produces higher quality.

```{r echo=FALSE}
ggplot(data = wine,
       aes(y = fixed.acidity, x = alcohol
       )) +
  geom_point(position='jitter',alpha = 0.5,color='orange') +
  scale_x_continuous(limits = c(9,13.5))+
  scale_y_continuous(limits = c(6,13))+
  geom_smooth(method = "lm",size=0.5,color='brown')  +
  facet_wrap(~quality_level) +
  scale_color_brewer(type='qual')
```

#####No obvious correlation 
####linear analysis:
##### Predict the wine quality based on chemical properties
```{r echo=FALSE}
m1<-lm(quality ~ volatile.acidity,data=wine)
m2<-update(m1,~. + alcohol)
m3<-update(m2,~. + sulphates)
m4<-update(m3,~. + citric.acid)
m5<-update(m4,~. + chlorides)
m6<-update(m5,~. + total.sulfur.dioxide)
m7<-update(m6,~. + density)
mtable(m1,m2,m3,m4,m5,m6,m7)
```
#####The model can be described as:wine_quality = 2.985 + 0.276xalcohol - 2.985xvolatile.acidity + 0.908xsulphates + 0.065xcitric.acid - -1.763*chlorides - 0.002xtotal.sulfur.dioxide

#####Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?
###### The density contribute little to quality level, but the alcohol has a negative influence on density. Higher quality wine have higher alcohol and sulphates. The influence of PH is not obvious. Residual sugar has little influence on quality. Lower total sulfur dioxide produces higher quality.

#####Were there any interesting or surprising interactions between features?

######From bivariate plot, we can find some variables, such as residual sugar have peaks with x-axis of quality, but when inserting other variables into analysis, the result show that residual sugar has little influence on quality.

#####OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

######The model can be described as:wine_quality = 2.985 + 0.276xalcohol - 2.985xvolatile.acidity + 0.908xsulphates + 0.065xcitric.acid - -1.763*chlorides - 0.002xtotal.sulfur.dioxide

------
  
# Final Plots and Summary
  
### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x = quality,y=alcohol,color=quality_level), data = wine)+
  geom_point(alpha=0.5,position = 'jitter')+
  stat_summary(fun.y = 'mean',
               geom = 'line',
               color='blue')+
  scale_color_brewer(type='seq')+
  ggtitle('Alcohol VS. Quality')
```

#### Description One
##### This data most lies in quality level of 5-7, and alcohol has an obvious positive influence on quality, the better quality , the higher alcohol percentage. The line is clearyly showed the trend.However, from the linear modeling anlysis, alcohol plays an important role, but only up to 27%, is not the only factor resulting the quality of wine.

### Plot Two
```{r echo=FALSE, Plot_Two}
p1<-
  ggplot(aes(x=quality_level,y=alcohol),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='brown')+
  xlab('quality_level')+
  ylab('alcohol')+
  ggtitle('Alcohol VS Quality_level')
p2<-
  ggplot(aes(x=quality_level,y=volatile.acidity),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='brown')+
  xlab('quality_level')+
  ylab('volatile.acidity')+
  ggtitle('Volatile.acidity VS Quality_level')
p3<-
  ggplot(aes(x=quality_level,y=sulphates),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='brown')+
  xlab('quality_level')+
  ylab('sulphates')+
  ggtitle('Sulphates VS Quality_level')
p4<-
  ggplot(aes(x=quality_level,y=citric.acid),data=wine)+
  geom_boxplot(alpha=0.5)+
  geom_jitter(alpha=0.3,color='brown')+
  xlab('quality_level')+
  ylab('citric.acid')+
  ggtitle('Citric.acid VS Quality_level')     
grid.arrange(p1,p2,p3,p4,ncol=2)


```

#### Description Two
##### At first, I used ggpair to find the most related variables with quality, and from the plot, it shows clearly how the variables influence quality, whether the correlation is positive or negative can be addressed from the trend. High quality has higher alcohol, lower volatile acid, higher sulphates, higher citric acid.

### Plot Three
```{r echo=FALSE, Plot_Three}
p1<-
  ggplot(aes(x = citric.acid, y = alcohol), data = wine) +
  geom_point(alpha=0.5,size=1,position = 'jitter')+
  scale_x_continuous(limits = c(0,0.65))+
  scale_y_continuous(limits = c(10,13))+
  facet_wrap(~quality_level)+
  geom_smooth(method = 'lm',color='black',size=0.5)+
  scale_color_brewer(type = 'qual')+
  xlab('citric.acid')+
  ylab('alcohol')+
  ggtitle('Citric.acid VS Alcohol')



p2<-
  ggplot(aes(x = sulphates, y = volatile.acidity), data = wine) +
  geom_point(alpha=0.7,size=1,position = 'jitter')+
  scale_x_continuous(limits = c(0.4,1.0))+
  scale_y_continuous(limits = c(0.4,1.2))+
  facet_wrap(~quality_level)+
  geom_smooth(method = 'lm',size=0.5)+
  scale_color_brewer(type = 'qual')+
  xlab('sulphates')+
  ylab('volatile.acidity')+
  ggtitle('Sulphates VS Volatile.acidity')


grid.arrange(p1,p2,ncol=1)
```

#### Description Three
#####In general, high quality wine tend to have higher alcohol and lower volatile acidity content. They also tend to have higher sulphate and higher critic acid content.


# Reflection
#####The red wine dataset contains 1,599 observation with 11 variables on the chemical properties. I focus on the correlation between chemical properties and quality, and explore which varibles has the most influence on quality, futhermore, when analyzing multivariate, I even figuerd out the correlations of different chemical  properties besides with quality. And, in the last, I made linear modeling in order to quantify the influence exactly. 

#####However, other chemical properties shows weak correlation with quality, either from visualization or statistic calculation. Wine quality is a complex problem, it is influenced by many factors, thus I used linear modeling to analyze it which is over simplified model.

#####In my opinion, the variables of wine are not very suitable for analyzing, since only 4 factors are proved to have correlation with quality. I propose that the data should be added some useful variables for further analysis, such as produce_place, temperature, water percent, environment, year.  Plus, most data of this data set is between quality level of 5-6, low quality, and high quality have small scale of data, we should be provided with more data of this level to have some deeper analysis.





