### Third Qualitative variable
```{r}
library(ggplot2)
pf<-read.csv('pseudo_facebook.tsv',sep='\t')
ggplot(aes(x=gender,y=age),
       data=subset(pf, !is.na(gender)))+geom_boxplot()+
  stat_summary(fun.y = mean,geom='point',shape=4)

ggplot(aes(x=age,y=friend_count),
       data=subset(pf,!is.na(gender)))+
  geom_line(aes(color=gender),stat = 'summary',fun.y=median)
```

###3
# Write code to create a new data frame,
# called 'pf.fc_by_age_gender', that contains
# information on each age AND gender group.

# The data frame should contain the following variables:

#    mean_friend_count,
#    median_friend_count,
#    n (the number of users in each age and gender grouping)

# Here is an example of the structure of your data frame. Your
# data values will be different. Note that if you are grouping by
# more than one variable, you will probably need to call the
# ungroup() function.
```{r}
library(dplyr)

age_group<-group_by(pf,age)
age_gender<-group_by(age_group,gender)
pf.fc_by_age_gender<-summarise(age_gender,
          friend_count_mean=mean(as.numeric(friend_count)),
          friend_count_median=median(as.numeric(friend_count)),
          n=n())
head(pf.fc_by_age_gender)
```
```{r}
library(dplyr)
pf.fc_by_age_gender<-pf %>%
  filter(!is.na(gender))%>%
  group_by(age,gender)%>%
  summarise(mean_friend_count=mean(friend_count),
            median_friend_count=median(friend_count),
            n=n())%>%
  ungroup()%>%
  arrange(age)
```


###4
# Create a line graph showing the
# median friend count over the ages
# for each gender. Be sure to use
# the data frame you just created,
# pf.fc_by_age_gender.
```{r}
ggplot(aes(x=age,y=median_friend_count),
       data=pf.fc_by_age_gender)+
  geom_line(aes(color=gender))
```

##7 reshaping data
```{r}
install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide<-dcast(pf.fc_by_age_gender,
                                age ~ gender,
                                value.var='median_friend_count')
head(pf.fc_by_age_gender.wide)
```

##8
# Plot the ratio of the female to male median
# friend counts using the data frame
# pf.fc_by_age_gender.wide.

# Think about what geom you should use.
# Add a horizontal line to the plot with
# a y intercept of 1, which will be the
# base line. Look up the documentation
# for geom_hline to do that. Use the parameter
# linetype in geom_hline to make the
# line dashed.
```{r}
ggplot(aes(x=age,y=female/male),
       data=pf.fc_by_age_gender.wide)+
  geom_line()+
  geom_hline(yintercept = 1, alpha=0.3,linetype=2)
```

###9
```{r}
pf$year_joined<-floor(2014-pf$tenure/365)
summary(pf$year_joined)
```

##10 cut a variable
```{r}
table(pf$year_joined)
pf$year_joined.bucket<-cut(pf$year_joined,
                           c(2004,2009,2011,2012,2014))
```

##11 plotting it all together 
# Create a line graph of friend_count vs. age
# so that each year_joined.bucket is a line
# tracking the median user friend_count across
# age. This means you should have four different
# lines on your plot.

# You should subset the data to exclude the users
# whose year_joined.bucket is NA.
```{r}
ggplot(aes(x=age,y=friend_count),
       data=subset(pf, !is.na(year_joined.bucket)))+
  geom_line(aes(color=year_joined.bucket),
            stat='summary',fun.y='median')
```
###plot the grand mean solution
```{r}
ggplot(aes(x=age,y=friend_count),
       data=subset(pf, !is.na(year_joined.bucket)))+
  geom_line(aes(color=year_joined.bucket),
            stat='summary',fun.y=mean)+
  geom_line(stat='summary',fun.y=mean,linetype=2)
```


##13
```{r}
with(subset(pf,tenure>=1),summary(friend_count/tenure))

```

##14

```{r}
# Create a line graph of mean of friendships_initiated per day (of tenure)
# vs. tenure colored by year_joined.bucket.

# You need to make use of the variables tenure,
# friendships_initiated, and year_joined.bucket.

# You also need to subset the data to only consider user with at least
# one day of tenure.
ggplot(aes(x=tenure,y=friendships_initiated/tenure),
       data=subset(pf,tenure>=1))+
         geom_line(aes(color=year_joined.bucket))
```
##15

```{r}
# Instead of geom_line(), use geom_smooth() to add a smoother to the plot.
# You can use the defaults for geom_smooth() but do color the line
# by year_joined.bucket
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))
```
#18
##histograms revisited 
```{r}
yo<-read.csv('yogurt.csv')
str(yo)

yo$is<- factor(yo$id)
str(yo)
```
```{r}

ggplot(aes(x=price),data=yo)+
 geom_histogram()
```

#19
##number of purchases 

```{r}
# Create a new variable called all.purchases,
# which gives the total counts of yogurt for
# each observation or household.

# One way to do this is using the transform
# function. You can look up the function transform
# and run the examples of code at the bottom of the
# documentation to figure out what it does.

# The transform function produces a data frame
# so if you use it then save the result to 'yo'!
summary(yo)
length(unique(yo$price))
table(yo$price)

```

```{r}
yo<-transform(yo,all.purchases=strawberry+blueberry+pina.colada+plain+mixed.berry)
```
#20
# Create a scatterplot of price vs time.

# This will be an example of a time series plot.

```{r}
ggplot(aes(x=time,y=price),data=yo)+
  geom_jitter(alpha=0.25,shape=21,fill=I('#F79420'))
```
#22
#looking at Samples of Households
```{r}
#set the seed for reproducible results
set.seed(4230)
sample.ids<-sample(levels(yo$id),16)
ggplot(aes(x=time,y=price),
       data=subset(yo,id %in% sample.ids))+
  facet_wrap(~id)+
  geom_line()+
  geom_point(aes(size=all.purchases),pch=1)
```
```{r}
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
pf_subset<-pf[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```
##generate a heat map
```{r}
nci<-read.table('nci.tsv')
colnames(nci)<-c(1:64)

library(reshape2)
nci.long.samp<-melt(as.matrix(nci[1:200.]))
names(nci.long.samp)<-c('gene','case','value')
head(nci.long.samp)

ggplot(aes(y=gene,x=case,fill=value),
       data=nci.long.samp)+
  geom_tile()+
  scale_fill_gradientn(colors=colorRampPalette(c('blue','red'))(100))
```
#1

```{r}
# Create a histogram of diamond prices.
# Facet the histogram by diamond color
# and use cut to color the histogram bars.

# The plot should look something like this.
# http://i.imgur.com/b5xyrOu.jpg
library(ggplot2)
ggplot(diamonds,aes(x=price,fill=cut))+
  geom_histogram(bin=50)+
  scale_fill_brewer(type='qual')+
  facet_wrap(~color)
```
#2


```{r}
# Create a scatterplot of diamond price vs.
# table and color the points by the cut of
# the diamond.
ggplot(aes(x=table,y=price,color=cut),data=diamonds)+
  geom_point(alpha=0.5)+
  scale_color_brewer(type='qual')
```


#3


```{r}
# Create a scatterplot of diamond price vs.
# volume (x * y * z) and color the points by
# the clarity of diamonds. Use scale on the y-axis
# to take the log10 of price. You should also
# omit the top 1% of diamond volumes from the plot.
diamonds$volume=diamonds$x*diamonds$y*diamonds$z
ggplot(subset(diamonds,volume<quantile(volume,0.99)),aes(x=volume,y=price,color=clarity))+
  geom_point(alpha=0.5)+
  scale_color_brewer(type='div')+
  scale_y_log10()
```
#5
```{r}
# Many interesting variables are derived from two or more others.
# For example, we might wonder how much of a person's network on
# a service like Facebook the user actively initiated. Two users
# with the same degree (or number of friends) might be very
# different if one initiated most of those connections on the
# service, while the other initiated very few. So it could be
# useful to consider this proportion of existing friendships that
# the user initiated. This might be a good predictor of how active
# a user is compared with their peers, or other traits, such as
# personality (i.e., is this person an extrovert?).

# Your task is to create a new variable called 'prop_initiated'
# in the Pseudo-Facebook data set. The variable should contain
# the proportion of friendships that the user initiated.


pf$prop_initiated<-pf$friendships_initiated/ifelse(pf$friend_count>0, pf$friend_count, 1)
```
#6
```{r}
# Create a line graph of the median proportion of
# friendships initiated ('prop_initiated') vs.
# tenure and color the line segment by
# year_joined.bucket.

# Recall, we created year_joined.bucket in Lesson 5
# by first creating year_joined from the variable tenure.
# Then, we used the cut function on year_joined to create
# four bins or cohorts of users.
pf$year_joined.bucket<-cut(pf$year_joined,
                           c(2004,2009,2011,2012,2014))
ggplot(aes(x=tenure,y=prop_initiated,color=year_joined.bucket),data=pf)+
  geom_line(stat='summary',fun.y=median)
```

#7
```{r}
# Smooth the last plot you created of
# of prop_initiated vs tenure colored by
# year_joined.bucket. You can bin together ranges
# of tenure or add a smoother to the plot.
ggplot(aes(x=tenure,y=prop_initiated,color=year_joined.bucket),data=pf)+
  geom_line(stat='summary',fun.y=median)+
  geom_smooth(color='black')
```

#9
```{r}
mean(pf$prop_initiated[pf$year_joined.bucket=='(2012,2014]'], na.rm=TRUE)
```
#10
```{r}
# Create a scatter plot of the price/carat ratio
# of diamonds. The variable x should be
# assigned to cut. The points should be colored
# by diamond color, and the plot should be
# faceted by clarity.
ggplot(aes(x=cut,y=price/carat,color=color),data=diamonds)+
  geom_point(position=position_jitter(),alpha=0.3)+
  facet_wrap(~clarity)+
  scale_color_brewer(type='div')
```

















